Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
phrs

\section{Capturing activity diaries}
There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.

>>>>

\section{Capturing activity diaries}

\subsection{Personal Electronic Sensors}
There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.
